---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# {lightning}

[![CRAN status](https://www.r-pkg.org/badges/version/lightning)](https://cran.r-project.org/package=lightning)

## Overview

{lightning} allows the user to generate deviates from different distributions.

{lightning} is a personal learning project. I wanted to learn more about Scala invocations using {sparklyr} and chose generating random deviates from distributions using the [RandomRDDs singleton object](https://github.com/apache/spark/blob/v3.1.1/mllib/src/main/scala/org/apache/spark/mllib/random/RandomRDDs.scala).

## Installation

You can install:

* the development version from [GitHub](https://github.com/nathaneastwood/lightning) with

```{r installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("nathaneastwood/lightning")
```

## Usage

{lightning} provides two methods for generating random variates. Firstly, we can generate N values from a `Distribution` class:

```{r distributions}
sc <- sparklyr::spark_connect(master = "local")

library(lightning)

norm <- Normal$new(sc = sc, size = 10L, num_partitions = 1L, seed = 1L)
norm$count()
norm$collect()
norm$first()
norm$get_num_partitions()
```

Secondly we can generate single values from a `Generator` class:

```{r generator}
norm_gen <- NormalGenerator$new(sc = sc)
norm_gen$set_seed(1L)
norm_gen$next_value()
```

## TODO

- Allow the ability to [`map()`](https://spark.apache.org/docs/2.4.3/api/java/org/apache/spark/rdd/RDD.html#map-scala.Function1-scala.reflect.ClassTag-) the distributions.
- Convert the RandomRDDs to a Spark `DataFrame`.

## Acknowledgments

[jozefhajnala](https://github.com/jozefhajnala) and [yitao-li](https://github.com/yitao-li) for their help on this topic.
